Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-26 code-tests.tex
double mach test.

The double mach reflection test is a classic test of hydrodynamical
algorithms, and was originally described in
\citet{1984JCoPh..54..115W} \citep[and more recently in][]{2008ApJS..178..137S}.

Problem type 4.  This is one of Alexei's test problems.  Tests
boundary conditions in hydro.  See Figure~\ref{fig.doublemach}.

>>>>

The double mach reflection test is a classic two-dimensional test of
hydrodynamic algorithms, and was originally described in
\citet{1984JCoPh..54..115W} \citep[and more recently
in][]{2008ApJS..178..137S}.  In this problem (shown in
Figure~\ref{fig.doublemach}), a shock is injected at an angle to a
reflecting surface, and a jet appears along the reflecting surface.
The ideal solution is self-similar, and the appearance of this
solution is highly sensitive to numerical diffusion.  If numerical
noise is present, a Kelvin-Helmholz instability develops along this
jet and breaks the self-similarity.

In the test problem shown in Figure~\ref{fig.doublemach}, a 2D
simulation with $960 \times 240$ cells was formed with a domain of $x
= [0, 4]$ and $y = [0, 1]$.  We use an ideal gas equation of state of
$\gamma = 1.4$, a pre-shock density of 1.4, and a pre-shock specific
internal energy of $2.5/1.4$ (all in arbitrary units).  A Mach 10
shock is initialized with a shock normal that is 30$^\circ$ from the
x-axis and an initial position on the lower boundary of x$ = 1/6$.
The lower y boundary and right x boundary are reflecting; the left x
boundary is inflowing, and the upper y boundary has a time-dependent
boundary condition that allows the shock to propagate into the domain
as if it extends to infinity.  The simulation starts at t$ = 0$ and
runs until t$ = 0.205$ (arbitrary units), at which point the rightmost
extent of the shock should be at roughly x$ = 3$.  In this run, we use
the direct Eulerian implementation of the piecewise parabolic hydro
method, with diffusion, flattening, and shock steepening all turned
on.

It is instructive to compare Figure~\ref{fig.doublemach} to Figure 9
in~\citet{1984JCoPh..54..115W}.  By the end of the simulation, a dense
jet is apparent at the leading edge of the shock, propagating along
the x-axis.  The shape of this jet is sensitive to numerical
diffusion, and our figure compares favorably to the higher-order
images from Woodward \& Colella.
